Community Analysis

### 2022-08-09 R/08-community-analysis.Rmd
convert pngs to svgs for poster and update some figure details

ggsave('Manuscript/fig3.jpg', p_beta, height = 2.5, width = 4)

@@

>>>>

ggsave('Manuscript/fig3.png', p_beta, height = 2.5, width = 4)

ggsave('Manuscript/fig3.svg', p_beta, height = 2.5, width = 4)

@@

ggsave('Manuscript/fig4.jpg', p_log10, width = 5, height = 5) 
ggsave('Manuscript/fig4.svg', p_log10, width = 5, height = 5)

## All
# ggsave("shared_taxa.png", p)
# ggsave("shared_taxa_log.png", p_log10, width = 5, height = 5)
